---
title: "PWHL Fantasy League - 2025/2026 Results"
author: "Alex & Noah"
---

```{r imports}
library(vctrs)
library(tidyverse)
library(gt)
library(bslib)
library(shiny)
library(bsicons)
library(ggimage)
library(rsvg)
library(janitor)
library(DescTools)

invisible(
  lapply(
    list.files(
      "./R",
      full.names = TRUE
    ),
    source
  )
)

pool <- 80
```

```{r "Get season dates and type"}
current_date <- today(
  tzone = "EST"
)

current_date = as.Date("2026-04-25")

seasons_dates_and_types <- get_seasons_dates_and_types()

season_dates_and_types <- seasons_dates_and_types["season_dates_and_types"][[1]]
season_schedules_by_id <- seasons_dates_and_types["season_schedules_by_id"][[1]]
season_schedules_by_year <- seasons_dates_and_types[
  "season_schedules_by_year"
][[1]]

days_for_current_date <- get_days_for_current_date(
  current_date,
  season_dates_and_types
)

next_game_day_date <- days_for_current_date$next_game_day_date |>
  as.character()
season_id <- days_for_current_date$season_id |>
  as.numeric()
season_id_for_schedule <- days_for_current_date$season_id_for_schedule |>
  as.numeric()
season_yr <- days_for_current_date$season_yr |>
  as.numeric()
game_type <- days_for_current_date$game_type |>
  as.character()
```

```{r "Get team data"}
team_data_frames <- get_all_teams(
  season_id,
  season_yr,
  game_type
)

team_logo_urls <- team_data_frames["team_logo_urls"][[1]]
teams <- team_data_frames["teams"][[1]]
team_codes <- team_data_frames["team_codes"][[1]]
all_teams <- team_data_frames["all_teams"][[1]]
```

```{r "Get schedule data"}
schedules <- get_schedule_info(
  season_id_for_schedule,
  season_schedules_by_id,
  team_codes,
  team_logo_urls,
  season_dates_and_types,
  next_game_day_date,
  current_date
)

schedule <- schedules["schedule"][[1]] |>
  mutate(
    game_date = game_date |> as.Date()
  )

schedule_to_date <- schedules["schedule_to_date"][[1]]
next_game_day_date <- schedules["next_game_day_date"][[1]]
todays_games <- schedules["todays_games"][[1]]
next_game_day <- schedules["next_game_day"][[1]]
```

```{r "Get Fantasy teams and standings"}
fantasy_teams_and_standings <- get_fantasy_teams_and_standings(
  all_teams,
  schedule_to_date,
  schedule,
  team_colours
)

team_images <- fantasy_teams_and_standings["team_images"][[1]]
team_colours <- fantasy_teams_and_standings["team_colours"][[1]]
team_rosters <- fantasy_teams_and_standings["team_rosters"][[1]]
roster_points_per_game <- fantasy_teams_and_standings[
  "roster_points_per_game"
][[1]]

fantasy_roster_points <- fantasy_teams_and_standings[
  "fantasy_roster_points"
][[1]] |>
  bind_rows(.id = "Team") |>
  mutate(
    team_image = paste0(
        "<img src='",
        team_images[Team],
        "' style='width:30px;height:30px;margin:0;'/>"
    ),
    team_colour = team_colours[Team]
  )

expanded_roster_stats <- fantasy_teams_and_standings[
  "expanded_roster_stats"
][[1]] |>
  compute_alt_awards() |>
  mutate(
    team_image = paste0(
        "<img src='",
        team_images[Team],
        "' style='width:30px;height:30px;margin:0;'/>"
    ),
    team_colour = team_colours[Team]
  )
```

```{r "Compute trade effectiveness"}
trade_results <- lapply(
  names(roster_points_per_game),
  function(team_name) {
    earned_points_from_trade <- roster_points_per_game[[team_name]] |>
      filter(
        !is.na(acquired) & acquired < game_id
      ) |> mutate(
        fantasy_points = sum(
          c(
            goals,
            assists,
            wins,
            wins,
            ot_losses
          )
        )
      ) |>
      slice(1) |>
      select(
        fantasy_points
      ) |>
      pull()

    lost_points_from_trade <- roster_points_per_game[[team_name]] |>
      filter(
        !is.na(let_go) & let_go < game_id
      ) |> mutate(
        fantasy_points = sum(
          c(
            goals,
            assists,
            wins,
            wins,
            ot_losses
          )
        )
      ) |>
      slice(1) |>
      select(
        fantasy_points
      ) |>
      pull()

    if (
      identical(
      earned_points_from_trade,
        numeric(0)
      )
    ) {
      earned_points_from_trade <- 0
    }

    if (
      identical(
      lost_points_from_trade,
        numeric(0)
      )
    ) {
      lost_points_from_trade <- 0
    }

    return(
      list(
        earned_points_from_trade = earned_points_from_trade,
        lost_points_from_trade = lost_points_from_trade
      )
    )
  }
)

trade_results <- data.frame(
  bind_rows(trade_results)
) |> mutate(
  Team = names(team_rosters)
)

trade_results <- trade_results |>
  mutate(
    trade_points = earned_points_from_trade - lost_points_from_trade,
    team_image = team_images[Team],
    team_image = paste0(
        "<img src='",
        team_image,
        "' style='width:30px;height:30px;margin:0;'/>"
    ),
    team_colour = team_colours[Team]
  ) |>
  arrange(-trade_points) |>
  relocate(
    Team
  )
```

```{r "Captaincy"}
captaincy <- data.frame(
  bind_rows(
    captains = c(2,1,2,4,1,3,2,2,3,3),
    assistant_captains = c(4,1,5,0,6,2,4,2,4,7),
    total = c(6,2,7,4,7,5,6,4,7,10)
  )
) |>
  mutate(
    Team = names(team_rosters),
    team_image = team_images[Team],
    team_image = paste0(
        "<img src='",
        team_image,
        "' style='width:30px;height:30px;margin:0;'/>"
    ),
    team_colour = team_colours[Team]
  ) |>
  arrange(
    -total
  )
```

```{r "Medians"}
df <- expanded_roster_stats %>%
  set_rownames(.$Team) |>
  select(
    -Team,
    -team_image,
    -team_colour
  )

median_counts <- sapply(
  df,
  function(x) rownames(df)[
    which.min(
      abs(
        x - median(x, na.rm = TRUE)
      )
    )
  ]
) |>
  vec_count() |>
  rename(
    Team = key,
    Medians = count
  ) |> mutate(
    team_image = paste0(
        "<img src='",
        team_images[Team],
        "' style='width:30px;height:30px;margin:0;'/>"
    ),
    team_colour = team_colours[Team]
  )

min_counts <- sapply(
  df,
  function(x) rownames(df)[which.min(x)]
) |>
  vec_count() |>
  rename(
    Team = key,
    Medians = count
  )

max_counts <- sapply(
  df,
  function(x) rownames(df)[which.max(x)]
) |>
  vec_count() |>
  rename(
    Team = key,
    Medians = count
  )
```

```{r "Draft summary"}

rosters_concat <- bind_rows(
  lapply(
    team_rosters,
    function (x) x |>
      distinct(
        player_name,
        .keep_all = TRUE
      )
  )
) |>
  mutate(
      player_headshot = paste0(
          "<img src='",
          player_headshot,
          "' style='width:50px;margin:0;border:1px solid",
          team_colour_1,
          ";border-radius:50%;'/>"
      ),
      team_logo = paste0(
          "<img src='",
          team_logo,
          "' style='width:30px;height:30px;margin:0;'/>"
      )
  ) |>
  select(
    team_logo,
    player_headshot,
    player_name,
    position
  )

goalie_drafts <- rosters_concat |>
  filter(
    position == "G"
  ) |>
  add_count(
    player_name
  ) |>
  arrange(
    -n
  ) |> distinct(
    player_name,
    .keep_all = TRUE
  ) |> select(
    -position
  )

forward_drafts <- rosters_concat |>
  filter(
    position == "F"
  ) |>
  add_count(
    player_name
  ) |>
  arrange(
    -n
  ) |> distinct(
    player_name,
    .keep_all = TRUE
  ) |> select(
    -position
  )

defender_drafts <- rosters_concat |>
  filter(
    position == "D"
  ) |>
  add_count(
    player_name
  ) |>
  arrange(
    -n
  ) |> distinct(
    player_name,
    .keep_all = TRUE
  ) |> select(
    -position
  )

rosters_concat_teams <- bind_rows(
  lapply(
    team_rosters,
    function (x) x |>
      distinct(
        player_name,
        .keep_all = TRUE
      )
  )
) |>
  mutate(
      team_logo = paste0(
          "<img src='",
          team_logo,
          "' style='width:30px;margin:0;'/>"
      )
  ) |>
  select(
    team_logo,
    team
  ) |> add_count(
    team
  ) |>
  arrange(
    -n
  ) |> distinct(
    team,
    .keep_all = TRUE
  )
```

## 🛼 MVP ⛸️ {transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}
```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
#| 
data <- fantasy_roster_points |>
  filter(player_id != -1, is.na(acquired), is.na(let_go)) |>
  arrange(desc(fantasy_points)) |>
  select(Team, first_name, last_name, fantasy_points) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = .7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```
:::

::: {.column .fragment .fade-right}


```{r}
fantasy_roster_points |>
  filter(player_id != -1, is.na(acquired), is.na(let_go)) |>
  arrange(desc(fantasy_points)) |>
  select(team_image, Team, first_name, last_name, fantasy_points) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_merge(columns = c(first_name, last_name)) |>
  cols_label(
    team_image = "",
    first_name = "Player",
    fantasy_points = "Points"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 🛼 LVBSAP (less valuable but still appreciated player...) ⛸️ {transition="zoom" transition-speed="slow"}
::: {.columns}

::: {.column .fragment .fade-right}
```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- fantasy_roster_points |>
  filter(player_id != -1, is.na(acquired), is.na(let_go)) |>
  arrange(fantasy_points) |>
  select(Team, first_name, last_name, fantasy_points) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```
::: 

::: {.column .fragment .fade-right}

```{r}
fantasy_roster_points |>
  filter(player_id != -1, is.na(acquired), is.na(let_go)) |>
  arrange(fantasy_points) |>
  select(team_image,Team, first_name, last_name, fantasy_points) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_merge(columns = c(first_name, last_name)) |>
  cols_label(
    team_image = "",
    first_name = "Player",
    fantasy_points = "Points"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 🟰 Team Equality Award 🟰 {transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}
```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- fantasy_roster_points |>
  filter(player_id != -1, is.na(acquired), is.na(let_go)) |>
  arrange(fantasy_points) |>
  select(Team, first_name, last_name, fantasy_points) |>
  group_by(Team) |>
  summarize(Gini = DescTools::Gini(fantasy_points)) |>
  arrange(Gini) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

::: {.column .fragment .fade-right}

```{r}
fantasy_roster_points |>
  filter(player_id != -1, is.na(acquired), is.na(let_go)) |>
  arrange(fantasy_points) |>
  select(Team, first_name, last_name, fantasy_points) |>
  group_by(Team) |>
  summarize(Gini = DescTools::Gini(fantasy_points)) |>
  arrange(Gini) |>
  mutate(
    team_image = paste0(
        "<img src='",
        team_images[Team],
        "' style='width:30px;height:30px;margin:0;'/>"
    ),
  ) |>
  relocate(
    team_image
  ) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = ""
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 🧠 Remembered the purpose of the game Award 🏒 {transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}

```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- expanded_roster_stats |>
  arrange(desc(goals)) |>
  select(Team, goals) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

::: {.column .fragment .fade-right}

```{r}
expanded_roster_stats |>
  arrange(desc(goals)) |>
  select(team_image,Team, goals) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    goals = "Goals"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 🫴 Best Helper Award 🫂 {transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}

```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- expanded_roster_stats |>
  arrange(desc(assists)) |>
  select(Team, assists) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

::: {.column .fragment .fade-right}

```{r}
expanded_roster_stats |>
  arrange(desc(assists)) |>
  select(team_image,Team, assists) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    assists = "Assists"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 😾 Battle not the war Award 🦾 {transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}

```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- expanded_roster_stats |>
  mutate(faceoff_pct = faceoff_wins / faceoff_attempts) |>
  arrange(desc(faceoff_pct)) |>
  select(Team, faceoff_pct) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

::: {.column .fragment .fade-right}

```{r}
expanded_roster_stats |>
  mutate(faceoff_pct = faceoff_wins / faceoff_attempts) |>
  arrange(desc(faceoff_pct)) |>
  select(team_image,Team, faceoff_pct) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    faceoff_pct = "Faceoff %"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::


## 🫡 Tryer Award 👍{transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}

```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- expanded_roster_stats |>
  arrange(desc(shots)) |>
  select(Team, shots) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

::: {.column .fragment .fade-right}


```{r}
expanded_roster_stats |>
  arrange(desc(shots)) |>
  select(team_image,Team, shots) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    shots = "Shots"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 🫡 Can't miss if you don't shoot Award 👎{transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}

```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- expanded_roster_stats |>
  arrange(shots) |>
  select(Team, shots) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

::: {.column .fragment .fade-right}


```{r}
expanded_roster_stats |>
  arrange(shots) |>
  select(team_image,Team, shots) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    shots = "Shots"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 🪑 Benchwarmer Award 🔥{transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}

```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- expanded_roster_stats |>
  arrange(time_on_ice) |>
  select(Team, time_on_ice) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::


::: {.column .fragment .fade-right}

```{r}
expanded_roster_stats |>
  arrange(time_on_ice) |>
  select(team_image,Team, time_on_ice) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    time_on_ice = "Time On Ice"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 🧊 Icewarmer Award 🔥{transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}

```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- expanded_roster_stats |>
  arrange(desc(time_on_ice)) |>
  select(Team, time_on_ice) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

::: {.column .fragment .fade-right}

```{r}
expanded_roster_stats |>
  arrange(desc(time_on_ice)) |>
  select(team_image,Team, time_on_ice) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    time_on_ice = "Time On Ice"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 🧠 Remembered the other purpose of the game Award ✅ {transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}

```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- expanded_roster_stats |>
  arrange(desc(wins)) |>
  select(Team, wins) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

::: {.column .fragment .fade-right}

```{r}
expanded_roster_stats |>
  arrange(desc(wins)) |>
  select(team_image,Team, wins) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    wins = "Wins"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 😬 It's not over til it's over Award 😣{transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}

```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- expanded_roster_stats |>
  arrange(desc(ot_losses)) |>
  select(Team, ot_losses) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.6
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

::: {.column .fragment .fade-right}

```{r}
expanded_roster_stats |>
  arrange(desc(ot_losses)) |>
  select(team_image,Team, ot_losses) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    ot_losses = "OT Losses"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 😫 Biggest Loser ✖️{transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}

```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- expanded_roster_stats |>
  arrange(wins) |>
  select(Team, wins) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

::: {.column .fragment .fade-right}

```{r}
expanded_roster_stats |>
  arrange(wins) |>
  select(team_image,Team, wins) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    wins = "Wins"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## ➕ In on the Action Award ➖{transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}

```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- expanded_roster_stats |>
  arrange(desc(plus_minus)) |>
  select(Team, plus_minus) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

::: {.column .fragment .fade-right}


```{r}
expanded_roster_stats |>
  arrange(desc(plus_minus)) |>
  select(team_image,Team, plus_minus) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    plus_minus = "Plus/Minus"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::


## 🙅‍♀️ Violence Award 🤼‍♀️{transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}

```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- expanded_roster_stats |>
  arrange(desc(penalty_minutes)) |>
  select(Team, penalty_minutes) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

::: {.column .fragment .fade-right}

```{r}
expanded_roster_stats |>
  arrange(desc(penalty_minutes)) |>
  select(team_image,Team, penalty_minutes) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    penalty_minutes = "Penalty Minutes"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 🧏‍♀️ Violence Lite Award 🤼‍♀️ {transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}

```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- expanded_roster_stats |>
  arrange(desc(hits)) |>
  select(Team, hits) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```
:::

::: {.column .fragment .fade-right}


```{r}
expanded_roster_stats |>
  arrange(desc(hits)) |>
  select(team_image,Team, hits) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    hits = "Hits"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::


## 🏒 Player-of-the-game Award 🧮 {transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}

```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- expanded_roster_stats |>
  arrange(desc(game_count)) |>
  select(Team, game_count) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

::: {.column .fragment .fade-right}

```{r}
expanded_roster_stats |>
  arrange(desc(game_count)) |>
  select(team_image,Team, game_count) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    game_count = "Games Played"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```
:::

:::

## 🏒 Watcher-of-the-game Award 👀 {transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}

```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
data <- expanded_roster_stats |>
  arrange(game_count) |>
  select(Team, game_count) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.6
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

::: {.column .fragment .fade-right}

```{r}
expanded_roster_stats |>
  arrange(game_count) |>
  select(team_image,Team, game_count) |>
  head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    game_count = "Games Played"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```
:::

:::

## 🔪 The Trader Award 🔁 {transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}
```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
#| 
data <- trade_results |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = .7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```
:::

::: {.column .fragment .fade-right}


```{r}
trade_results |>
  head(3) |>
  select(
    team_image,
    Team,
    trade_points
  ) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    trade_points = "Trade Points"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 📊 Mediocrity Award 🟰 {transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}
```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
#| 
data <- median_counts |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = .7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```
:::

::: {.column .fragment .fade-right}


```{r}
median_counts |>
  head(3) |>
  select(
    team_image,
    Team,
    Medians
  ) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = ""
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 👩‍🍳 Too many cooks Award 🧂 {transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}
```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
#| 
data <- captaincy |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.6
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```
:::

::: {.column .fragment .fade-right}


```{r}
captaincy |>
  head(3) |>
  select(
    team_image,
    Team,
    captains,
    assistant_captains,
    total
  ) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    captains = "Captains",
    assistant_captains = "Assistant Captains",
    total = "Total"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 🏆 ...and the winner is... 🏅{transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}
```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
#| 
ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = teams |> filter(
      team_code == "MIN"
    ) |> select(
      colour_1
    ) |>
    pull()
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_logo_urls$MIN
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

:::


## 🏆 ...and the winner is... 🏅{transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column .fragment .fade-right}
```{r}
#| dev: png
#| dev-args: !expr list(bg = "transparent")
#| 
data <- fantasy_roster_points |>
  filter(player_id == -1) |>
  arrange(desc(fantasy_points)) |>
  select(Team, fantasy_points) |>
  head(1)

ggplot() +
  geom_point(
    aes(x = 0, y = 0),
    size = 160,
    colour = team_colours[[data$Team]]
  ) +
  geom_image(
    aes(
      x = 0,
      y = 0,
      image = team_images[[data$Team]]
    ),
    size = 0.7
  ) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent"),
    legend.box.background = element_rect(fill = "transparent")
  )
```

:::

::: {.column .fragment .fade-right}

```{r}
fantasy_roster_points |>
  filter(player_id == -1) |>
  arrange(desc(fantasy_points)) |>
  select(team_image,Team, fantasy_points) |>
  # head(3) |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_image
      )
  ) |>
  cols_label(
    team_image = "",
    fantasy_points = "Fantasy Points"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 📊 Draft Summary 📝 {transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column width="33%" .fragment .fade-right}

```{r}
forward_drafts |>
  head(
    min(
      nrow(forward_drafts),
      nrow(defender_drafts),
      nrow(goalie_drafts),
      7
    )
  ) |>
  gt() |>
  fmt_markdown(
      columns = c(
          player_headshot,
          team_logo
      )
  ) |>
  cols_label(
    team_logo = "",
    player_headshot = "",
    player_name = "Forwards",
    n = "Drafts"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

::: {.column width="33%" .fragment .fade-right}

```{r}
defender_drafts |>
  head(
    min(
      nrow(forward_drafts),
      nrow(defender_drafts),
      nrow(goalie_drafts),
      7
    )
  ) |>
  gt() |>
  fmt_markdown(
      columns = c(
          player_headshot,
          team_logo
      )
  ) |>
  cols_label(
    team_logo = "",
    player_headshot = "",
    player_name = "Defenders",
    n = "Drafts"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

::: {.column width="33%" .fragment .fade-right}

```{r}
goalie_drafts |>
  head(
    min(
      nrow(forward_drafts),
      nrow(defender_drafts),
      nrow(goalie_drafts),
      7
    )
  ) |>
  gt() |>
  fmt_markdown(
      columns = c(
          player_headshot,
          team_logo
      )
  ) |>
  cols_label(
    team_logo = "",
    player_headshot = "",
    player_name = "Goalies",
    n = "Drafts"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::

## 📊 Draft Summary 📝 {transition="zoom" transition-speed="slow"}

::: {.columns}

::: {.column width="100%" .fragment .fade-right}

```{r}
rosters_concat_teams |>
  gt() |>
  fmt_markdown(
      columns = c(
          team_logo
      )
  ) |>
  cols_label(
    team_logo = "",
    team = "Team",
    n = "Drafts"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }"
  )
```

:::

:::