---
title: "PWHL Fantasy League - 2025/2026 Results"
author: "Alex & Noah"
format: revealjs
---

```{r imports}
library(tidyverse)
library(gt)
library(bslib)
library(shiny)
library(bsicons)
library(ggimage)
library(rsvg)
library(janitor)

invisible(
  lapply(
    list.files(
      "./R",
      full.names = TRUE
    ),
    source
  )
)

pool <- 80
```

```{r "Get season dates and type"}
current_date = today(
  tzone = "EST"
)

current_date = as.Date("2026-04-24")

seasons_dates_and_types <- get_seasons_dates_and_types()

season_dates_and_types <- seasons_dates_and_types["season_dates_and_types"][[1]]
season_schedules_by_id <- seasons_dates_and_types["season_schedules_by_id"][[1]]
season_schedules_by_year <- seasons_dates_and_types[
  "season_schedules_by_year"
][[1]]

days_for_current_date <- get_days_for_current_date(
  current_date,
  season_dates_and_types
)

next_game_day_date <- days_for_current_date$next_game_day_date |>
  as.character()
season_id <- days_for_current_date$season_id |>
  as.numeric()
season_id_for_schedule <- days_for_current_date$season_id_for_schedule |>
  as.numeric()
season_yr <- days_for_current_date$season_yr |>
  as.numeric()
game_type <- days_for_current_date$game_type |>
  as.character()
```

```{r "Get team data"}
team_data_frames <- get_all_teams(
  season_id,
  season_yr,
  game_type
)

team_logo_urls <- team_data_frames["team_logo_urls"][[1]]
teams <- team_data_frames["teams"][[1]]
team_codes <- team_data_frames["team_codes"][[1]]
all_teams <- team_data_frames["all_teams"][[1]]
```

```{r "Get schedule data"}
schedules <- get_schedule_info(
  season_id_for_schedule,
  season_schedules_by_id,
  team_codes,
  team_logo_urls,
  season_dates_and_types,
  next_game_day_date,
  current_date
)

schedule <- schedules["schedule"][[1]] |>
  mutate(
    game_date = game_date |> as.Date()
  )

schedule_to_date <- schedules["schedule_to_date"][[1]]
next_game_day_date <- schedules["next_game_day_date"][[1]]
todays_games <- schedules["todays_games"][[1]]
next_game_day <- schedules["next_game_day"][[1]]
```

```{r "Get Fantasy teams and standings"}
fantasy_teams_and_standings <- get_fantasy_teams_and_standings(
  all_teams,
  schedule_to_date,
  schedule,
  team_colours
)

team_images <- fantasy_teams_and_standings["team_images"][[1]]
team_colours <- fantasy_teams_and_standings["team_colours"][[1]]
team_rosters <- fantasy_teams_and_standings["team_rosters"][[1]]
roster_points_per_game <- fantasy_teams_and_standings[
  "roster_points_per_game"
][[1]]
fantasy_roster_points <- fantasy_teams_and_standings[
  "fantasy_roster_points"
][[1]]
expanded_roster_stats <- fantasy_teams_and_standings[
  "expanded_roster_stats"
][[1]]

standings <- compute_standings_changes_indicator(
  all_teams,
  schedule_to_date,
  current_date,
  schedule,
  fantasy_teams_and_standings["standings"][[1]]
)
```

## Categories

- 🛼 Most/least points per player ⛸️
- 🏒 Most/least points per category 🥅
- 😤 Most penalty minutes 🤬
- 💪 Most hits 🤼‍♀️
- 📈 Draft summary 📉
- 🔄️ Best/worst trades 🔄️
- 🏆 Overall winner 🏅

## 🛼 Points per player ⛸️

:::: {.columns}

::: {.column width="50%"}
Most
:::

::: {.column width="50%"}
Least
:::

::::


## 🏒 Points per category 🥅

:::: {.columns}

::: {.column width="25%"}
Goals
:::

::: {.column width="25%"}
Assists
:::

::: {.column width="25%"}
Wins
:::

::: {.column width="25%"}
Overtime losses
:::

::::


## 😤 Penalty minutes (by team) 🤬

:::: {.columns}

::: {.column width="50%"}
PWHL Teams
:::

::: {.column width="50%"}
Fantasy Teams
:::

::::


## 💪 Hits (by team) 🤼‍♀️

:::: {.columns}

::: {.column width="50%"}
PWHL Teams
:::

::: {.column width="50%"}
Fantasy Teams
:::

::::


## 📈 Draft summary 📉

Hi


## 🔄️ Trades 🔄️

Hi


## 🏆 ...and the winner is... 🏅

:::: {.columns}

::: {.column width="50%"}
PWHL Teams
:::

::: {.column width="50%"}
Fantasy Teams
:::

::::