```{r imports}
library(tidyverse)
library(gt)
library(bslib)
library(shiny)
library(bsicons)
library(ggimage)

invisible(
  lapply(
    list.files(
      "./R",
      full.names = TRUE
    ),
    source
  )
)
```

```{r "Get season dates and type"}
current_date = today()
current_date = "2025-04-22"

season_dates_and_type <- get_season_dates_and_type()

days_for_current_date <- get_days_for_current_date(
  current_date,
  season_dates_and_type
)

last_game_day_date <- days_for_current_date$last_game_day_date |>
  as.character()
next_game_day_date <- days_for_current_date$next_game_day_date |>
  as.character()
season_id <- days_for_current_date$season_id |>
  as.numeric()
season <- days_for_current_date$season |>
  as.numeric()
game_type <- days_for_current_date$game_type |>
  as.character()
```

```{r "Get team and schedule data"}
team_data_frames <- get_all_teams(
  season_id,
  season,
  game_type
)

team_logo_urls <- team_data_frames["team_logo_urls"][[1]]
teams <- team_data_frames["teams"][[1]]
team_codes <- team_data_frames["team_codes"][[1]]
all_teams <- team_data_frames["all_teams"][[1]]

schedules <- get_schedule(
  season_id,
  team_codes,
  team_logo_urls,
  season_dates_and_type,
  last_game_day_date,
  next_game_day_date,
  current_date
)

schedule <- schedules["schedule"][[1]] |>
    mutate(
        game_date = game_date |> as.Date()
    )

schedule_to_date <- schedules["schedule_to_date"][[1]]
last_game_day_date <- schedules["last_game_day_date"][[1]]
next_game_day_date <- schedules["next_game_day_date"][[1]]
last_game_day <- schedules["last_game_day"][[1]]
next_game_day <- schedules["next_game_day"][[1]]
```

```{r "Get Fantasy teams and standings"}
fantasy_teams_and_standings <- get_fantasy_teams_and_standings(
  all_teams,
  schedule_to_date,
  schedule
)

team_images <- fantasy_teams_and_standings["team_images"][[1]]
team_rosters <- fantasy_teams_and_standings["team_rosters"][[1]]
roster_points_per_game <- fantasy_teams_and_standings[
  "roster_points_per_game"
][[1]]
standings <- fantasy_teams_and_standings["standings"][[1]]

if (typeof(last_game_day) != "logical") {
  last_game_day <- last_game_day |>
    mutate(
      roster_points_per_game[game_id, ]
    )
}
```

# Overview

## Row

```{r "next game day"}
p_args <- next_game_day |>
  mutate(
    temp = paste0(
      home_team_code,
      " @ ",
      away_team_code,
      ", ",
      game_status
    )
  ) |>
  select(
    temp
  )

p_args <- map(
  p_args[, 1],
  p
)

value_box(
  title = "Next game day",
  showcase = bs_icon(
    "calendar-event",
    size = "6vh"
  ),
  value = tags$p(
    format(
      as.Date(
        next_game_day_date,
        format = "%Y-%m-%d"
      ),
      "%b %e, %Y"
    ),
    style = "font-size: 4vh;"
  ),
  theme = "success",
  !!!p_args
)
```

```{r "last game day"}
if (
  nrow(
    roster_points_per_game
  ) ==
    0
) {
  value_box(
    title = "No data available",
    showcase = bs_icon(
      "hourglass-split",
      size = "6vh"
    ),
    value = tags$p(
      "No games played yet this season",
      style = "font-size: 4vh;"
    ),
    theme = "danger"
  )
} else {
  last_game_day |>
    mutate(
      temp = "-"
    ) |>
    select(
      c(
        "home_team_code",
        "home_team_logo",
        "home_score",
        "temp",
        "away_score",
        "away_team_logo",
        "away_team_code"
      )
    ) |>
    gt() |>
    tab_header(
      format(
        last_game_day_date,
        "Last game day (%B %e, %Y)"
      )
    ) |>
    text_transform(
      locations = cells_body(
        columns = c(
          "home_team_logo",
          "away_team_logo"
        )
      ),
      fn = function(x) {
        web_image(
          url = x,
          height = "5vh"
        )
      }
    ) |>
    cols_label(
      home_team_code = "",
      home_team_logo = "Home",
      home_score = "",
      temp = "",
      away_score = "",
      away_team_logo = "Away",
      away_team_code = ""
    )
}

```

## Row

```{r "standings overview"}
#| title: "Standings"
standings |>
  mutate(
    delta = roster_points_per_game |>
      filter(
        game_date == last_game_day_date
      ) |>
      compute_standings(
        team_images
      ) |>
      pull(
        Points
      )
  ) |>
  mutate(
    Points = paste0(
      Points,
      " (+",
      delta,
      ")"
    )
  ) |>
  select(
    c(
      Name,
      Team,
      Points
    )
  ) |>
  gt() |>
  text_transform(
    locations = cells_body(
      columns = Team
    ),
    fn = function(x) {
      web_image(
        url = x,
        height = "5vh"
      )
    }
  )
```

# Team Standings

## Row

```{r "standings full"}
#| title: "Standings"
standings |>
  gt() |>
  text_transform(
    locations = cells_body(
      columns = Team
    ),
    fn = function(x) {
      web_image(
        url = x,
        height = "5vh"
      )
    }
  )
```

## Row

```{r "standings over time"}
#| title: "Standings over time"

if (
  nrow(
    roster_points_per_game
  ) ==
    0
) {
  value_box(
    title = "No data available",
    showcase = bs_icon(
      "hourglass-split",
      size = "6vh"
    ),
    value = tags$p(
      "No games played yet this season",
      style = "font-size: 4vh;"
    ),
    theme = "danger"
  )
} else {
  data <- roster_points_per_game |>
    mutate(
      across(
        names(team_rosters),
        ~ .x |> as.numeric() |> cumsum()
      ),
      game_idx = 1:nrow(
        roster_points_per_game
      )
    ) |>
    pivot_longer(
      cols = names(team_rosters),
      names_to = "Team",
      values_to = "Points"
    ) |>
    rename("Game" = game_idx)

  #TODO this needs to be moved ig
  standings <- standings |>
    mutate(
      colours = c("#5F259F", "#9d6dd1ff", "#2B2D42", "#F5F5F5")
    )

  data |>
    ggplot() +
    geom_line(
      aes(
        x = Game,
        y = Points,
        colour = Team
      ),
      linewidth = 2
    ) +
    scale_color_manual(values = standings$colours) +
    geom_point(
      data = standings,
      aes(
        x = max(data$Game),
        y = Points,
        colour = Name
      ),
      size = 10,
      colour = standings$colours
    ) +
    geom_image(
      data = standings,
      aes(
        x = max(data$Game),
        y = Points,
        image = Team
      )
    ) +
    guides(colour = guide_legend(override.aes = list(size = 10))) +
    theme_minimal()
}
```

# Team Rosters

::: {.panel-tabset}

```{r "team rosters"}
#| output: asis
res <- purrr::map_chr(
  unique(names(team_rosters)),
  function(name) {
    knitr::knit_child(
      text = c(
        "## `r name`",
        "",
        "```{r}",
        "#| echo: false",
        "html(",
        "    web_image(",
        "        url = team_images[[name]],",
        "        height = '50px'",
        "    )",
        ")",
        "team_rosters[[name]] |>",
        "    select(",
        "        c(",
        "            'jersey_number',",
        "            'player_headshot',",
        "            'player_name',",
        "            'position',",
        "            'primary_hand',",
        "            'dob',",
        "            'home_town'",
        "        )",
        "    ) |>",
        "    rename(",
        "        c(",
        "            '#' = 'jersey_number',",
        "            Headshot = 'player_headshot',",
        "            Name = 'player_name',",
        "            Pos = 'position',",
        "            Shoots = 'primary_hand',",
        "            DOB = 'dob',",
        "            'Home town' = 'home_town'",
        "        )",
        "    ) |>",
        "   gt() |>",
        "   text_transform(",
        "        locations = cells_body(columns = Headshot),",
        "        fn = function(x) {",
        "            web_image(",
        "                url = x,",
        "                height = '50px'",
        "            )",
        "        }",
        "    )",
        "```",
        "",
        ""
      ),
      envir = environment(),
      quiet = TRUE
    )
  }
)

cat(res, sep = '\n')
```
:::

# Schedule

```{r "Schedule"}

schedule |>
    select(
        c(
            game_date,
            game_status,
            away_team_logo,
            # away_team_code,
            away_score,
            home_team_logo,
            # home_team_code,
            home_score,
            venue
        )
    ) |>
    mutate(
        game_date = as.Date(
                game_date,
                format="%Y-%m-%d"
            ) |>
            format(
                "%a, %b %e"
            )
    ) |>
    gt() |>
    fmt_image(
        columns = c(
            away_team_logo,
            home_team_logo
        ),
        # width = "1.5em",
        height = "2em"
    ) |>
    cols_align(
        align = "center",
        columns = c(
            game_status,
            away_score,
            home_score
        )
    ) |>
    cols_width(
        game_date ~ pct(20),
        game_status ~ pct(20)
    ) |>
    cols_label(
        game_date = "Date",
        game_status = "Time",
        away_team_logo = "Away",
        # away_team_code = "",
        away_score = "Score",
        home_team_logo = "Home",
        # home_team_code = "",
        home_score = "Score",
        venue = "Venue"
    )
```

# PWHL Rosters

## Row {.tabset .landscape}

```{r "Boston roster"}
#| title: Boston
generate_pwhl_roster_gt_table(
  all_teams,
  "Boston"
)
```

```{r "Minnesota roster"}
#| title: Minnesota
generate_pwhl_roster_gt_table(
  all_teams,
  "Minnesota"
)
```

```{r "Montreal roster"}
#| title: Montreal
generate_pwhl_roster_gt_table(
  all_teams,
  "Montreal"
)
```

```{r "New York roster"}
#| title: New York
generate_pwhl_roster_gt_table(
  all_teams,
  "New York"
)
```

```{r "Ottawa roster"}
#| title: Ottawa
generate_pwhl_roster_gt_table(
  all_teams,
  "Ottawa"
)
```

```{r "Toronto roster"}
#| title: Toronto
generate_pwhl_roster_gt_table(
  all_teams,
  "Toronto"
)
```

