```{r imports}
library(tidyverse)
library(gt)
library(bslib)
library(shiny)
library(bsicons)
library(ggimage)
library(rsvg)

invisible(
  lapply(
    list.files(
      "./R",
      full.names = TRUE
    ),
    source
  )
)
 
current_date <- today(
  tzone = "EST"
)

current_date <- as.Date("2026-04-25")
# current_date <- as.Date("2025-11-15")
# current_date <- as.Date("2026-01-26")

season_schedules_by_id <- get_season_schedules_by_id()

season_id <- get_season_id_of_current_date(
  current_date,
  season_schedules_by_id
)

current_schedule <- season_schedules_by_id[[
  season_id
]]$schedule

next_game_day <- current_schedule |>
  filter(
    current_date <= game_date
  ) |>
  first() |>
  select(
    game_date
  ) |>
  pull()

team_info <- get_team_info(
  season_id
)

team_stats <- get_team_stats(
  season_id,
  team_info
)

player_boxes_per_game <- get_player_boxes_per_game(
  current_schedule
)

fantasy_teams <- get_fantasy_teams(
  current_schedule,
  current_date,
  team_stats,
  player_boxes_per_game
)

standings <- compute_standings(
  fantasy_teams
)
```

# Overview

## Row

```{r "todays games"}

todays_games <- current_schedule |>
  filter(
    game_date == current_date
  ) |> merge(
    team_info %>%
      rename_with(
        ~paste0(
          "home_",
          .
        )
      ),
    by.x = "home_team",
    by.y = "home_team_label"
  ) |> merge(
    team_info %>%
      rename_with(
        ~paste0(
          "away_",
          .
        )
      ),
    by.x = "away_team",
    by.y = "away_team_label"
  )

if (
  nrow(
    todays_games
  ) ==
    0
) {
  value_box(
    title = "No data available",
    showcase = bs_icon(
      "hourglass-split",
      size = "6vh"
    ),
    value = tags$p(
      "No games today :(",
      style = "font-size: 4vh;"
    ),
    theme = "danger"
  )
} else {
  todays_games |>
    mutate(
      temp = "-"
    ) |>
    select(
      c(
        "away_team_code",
        "away_team_logo",
        "away_score",
        "game_status",
        "home_score",
        "home_team_logo",
        "home_team_code"
      )
    ) |>
    gt() |>
    cols_align(
      align = "center",
      columns = everything()
    ) |>
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_body(
        columns = game_status
      )
    ) |>
    tab_header(
      format(
        current_date,
        "Today's games (%B %e, %Y)"
      )
    ) |>
    text_transform(
      locations = cells_body(
        columns = c(
          "away_team_logo",
          "home_team_logo"
        )
      ),
      fn = function(x) {
        web_image(
          url = x,
          height = "5vh"
        )
      }
    ) |>
    cols_label(
      away_team_code = "",
      away_team_logo = "Away",
      away_score = "",
      game_status = "",
      home_score = "",
      home_team_logo = "Home",
      home_team_code = ""
    ) |>
    tab_options(
      table.background.color = "#F5F5F5",
      column_labels.background.color = "#2B2D42",
      table.font.size = px(16),
      table.border.top.color = "transparent",
      table.border.bottom.color = "transparent",
      table_body.hlines.color = "transparent",
      table_body.border.bottom.color = "transparent",
      column_labels.border.bottom.color = "transparent",
      column_labels.border.top.color = "transparent"
    ) |>
    tab_style_body(
      style = cell_borders(
        sides = c("top", "right", "left", "bottom"),
        weight = px(0) # Remove row borders
      ),
      fn = function(x) {
        is.numeric(x) | is.character(x)
      }
    ) |>
    opt_css(
      css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }

    .gt_col_heading {
      position: sticky !important;
      top: 0px !important;
      z-index: 10 !important;
    }
    "
    )
}
```

## Row

```{r "standings overview"}
#| title: "Standings (with today's changes)"

standings |>
  mutate(
    fantasy_points = paste0(
      round(
        fantasy_points,
        2
      ),
      " (+",
      round(
        fantasy_points_change_since_yesterday,
        2
      ),
      ")"
    ),
    position_change_since_yesterday = case_when(
      position_change_since_yesterday == "-1" ~ "arrow-down",
      position_change_since_yesterday == "0" ~ NA,
      position_change_since_yesterday == "1" ~ "arrow-up"
    )
  ) |>
  gt() |>
  fmt_icon(
    columns = position_change_since_yesterday,
    fill_color = c(
      "arrow-up" = "#128800ff",
      "arrow-down" = "#c50101ff",
      height = "1.5em"
    )
  ) |>
  text_transform(
    locations = cells_body(
      columns = team_image
    ),
    fn = function(x) {
      web_image(
        url = x,
        height = "5vh"
      )
    }
  ) |>
  tab_style(
    style = list(
      cell_fill(
        color = from_column(
          column = "team_colour"
        )
      ),
      cell_text(
        weight = "bold"
      )
    ),
    locations = cells_body(
      columns = team_image
    )
  ) |>
  cols_hide(
    c(
      team_colour,
      fantasy_points_change_since_yesterday
    )
  ) |>
  cols_move(
    columns = c(
      fantasy_team_name,
      position_change_since_yesterday,
      fantasy_points
    ),
    after = team_image
  ) |>
  cols_label(
    team_image = "",
    fantasy_team_name = "Team Name",
    position_change_since_yesterday = "",
    fantasy_points = "Points"
  ) |>
  cols_align(
    columns = everything(),
    align = "center"
  ) |>
  sub_missing(
    columns = everything(),
    rows = everything(),
    missing_text = ""
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }

    .gt_col_heading {
      position: sticky !important;
      top: 0px !important;
      z-index: 10 !important;
    }
    "
  )
```

## Row

```{r "trades"}

trades_df <- fantasy_teams |>
  map(
    `[[`,
    1
  ) |>
  bind_rows() |> mutate(
    team_name = names(
      fantasy_teams
    )
  ) |>
  filter(
    !is.na(trade_date)
  )
  

player_headshots <- bind_rows(
  team_stats |>
    map(
      `[[`,
      1
    ) |>
    bind_rows() |>
    select(
      name,
      player_headshot,
      team_id
    ),
  team_stats |>
    map(
      `[[`,
      2
    ) |>
    bind_rows() |>
    select(
      name,
      player_headshot,
      team_id
    )
)



if (
  nrow(
    trades_df
  ) ==
    0
) {
  value_box(
    title = "Trades",
    showcase = bs_icon(
      "arrow-left-right",
      size = "6vh"
    ),
    value = tags$p(
      "No trades yet",
      style = "font-size: 4vh;"
    ),
    theme = "danger"
  )
} else {
  trades_df |>
    merge(
      player_headshots |>
        rename(
          new_player_headshot = player_headshot,
          new_player_team_id = team_id
        ),
      by.x = "new_player",
      by.y = "name"
    ) |>
    merge(
      team_info |>
        select(
          team_id,
          colours_1
        ) |>
        rename(
          new_player_colours_1 = colours_1
        ),
      by.x = "new_player_team_id",
      by.y = "team_id"
    ) |>
    merge(
      player_headshots |>
        rename(
          old_player_headshot = player_headshot,
          old_player_team_id = team_id
        ),
      by.x = "old_player",
      by.y = "name"
    ) |>
    merge(
      team_info |>
        select(
          team_id,
          colours_1
        ) |>
        rename(
          old_player_colours_1 = colours_1
        ),
      by.x = "old_player_team_id",
      by.y = "team_id"
    ) |>
    mutate(
      new_player_headshot = paste0(
        "<img src='",
        new_player_headshot,
        "' style='width:50px;height:50px;border:1px solid",
        new_player_colours_1,
        ";border-radius:50%;'/>"
      ),
      old_player_headshot = paste0(
        "<img src='",
        old_player_headshot,
        "' style='width:50px;height:50px;border:1px solid",
        old_player_colours_1,
        ";border-radius:50%;'/>"
      )
    ) |>
    select(
      c(
        team_image,
        trade_date,
        new_player_headshot,
        new_player,
        old_player_headshot,
        old_player,
        team_colour
      )
    ) |>
    gt() |>
    fmt_markdown(
      columns = c(
        new_player_headshot,
        old_player_headshot
      )
    ) |>
    text_transform(
      locations = cells_body(
        columns = team_image
      ),
      fn = function(x) {
        web_image(
          url = x,
          height = "5vh"
        )
      }
    ) |>
    tab_style(
      style = list(
        cell_fill(
          color = from_column(
            column = "team_colour"
          )
        ),
        cell_text(
          weight = "bold"
        )
      ),
      locations = cells_body(
        columns = team_image
      )
    ) |>
    cols_hide(
      team_colour
    ) |>
    cols_align(
      columns = everything(),
      align = "center"
    ) |>
    cols_label(
      team_image = "",
      trade_date = "Date",
      new_player_headshot = "",
      new_player = "Acquired",
      old_player_headshot = "",
      old_player = "Let go"
    ) |>
    tab_header(
      "Trades"
    ) |>
    tab_options(
      table.background.color = "#F5F5F5",
      column_labels.background.color = "#2B2D42",
      table.font.size = px(16),
      table.border.top.color = "transparent",
      table.border.bottom.color = "transparent",
      table_body.hlines.color = "transparent",
      table_body.border.bottom.color = "transparent",
      column_labels.border.bottom.color = "transparent",
      column_labels.border.top.color = "transparent"
    ) |>
    tab_style_body(
      style = cell_borders(
        sides = c("top", "right", "left", "bottom"),
        weight = px(0) # Remove row borders
      ),
      fn = function(x) {
        is.numeric(x) | is.character(x)
      }
    ) |>
    opt_css(
      css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }

    .gt_col_heading {
      position: sticky !important;
      top: 0px !important;
      z-index: 10 !important;
    }
    "
    )
}
```

## Row

```{r "next game day"}
p_args <- next_game_day |>
  mutate(
    temp = paste0(
      home_team_code,
      " @ ",
      away_team_code,
      ", ",
      game_status
    )
  ) |>
  select(
    temp
  )

p_args <- map(
  p_args[, 1],
  p
)

value_box(
  title = "Next game day",
  showcase = bs_icon(
    "calendar-event",
    size = "6vh"
  ),
  value = tags$p(
    format(
      as.Date(
        next_game_day_date,
        format = "%Y-%m-%d"
      ),
      "%b %e, %Y"
    ),
    style = "font-size: 4vh;"
  ),
  theme = "success",
  !!!p_args
)
```

## Row

```{r "prize pool thermometer"}
temps <- data.table(temp = seq(from = 0, to = pool, by = 0.01))
temps[, temp1 := shift(temp, 1)]

ggplot(temps, aes(x = 1)) +
  geom_segment(
    aes(y = 0, yend = 10 * length(team_rosters)),
    linewidth = 10,
    lineend = c("round"),
    color = "black"
  ) +
  geom_segment(
    aes(y = 0, yend = 10 * length(team_rosters)),
    linewidth = 9,
    lineend = c("round"),
    color = "white"
  ) +
  geom_segment(
    data = temps[1:1000],
    aes(y = temp, yend = temp1),
    color = "#5F259F",
    lineend = c("round"),
    linewidth = 9
  ) +
  geom_segment(
    data = temps[-(1:1000)],
    aes(y = temp, yend = temp1),
    color = "#5F259F",
    lineend = c("square"),
    linewidth = 9
  ) +
  theme_void() +
  labs(
    title = paste0("Prize pool: ", pool, "$")
  ) +
  theme(
    plot.title = element_text(size = 50, hjust = 0.5)
  ) +
  coord_flip()
```

## Row

Need help making your team? Generate a random regulation team [here](#team-generator) to paste into the [Google Sheet](https://docs.google.com/spreadsheets/d/1sywjZ6quCmbLBq_wEEXZEDzcW0NeBpCtRaT3W1hDkhI/edit?usp=sharing)

## Row

```{r "Text: last update (data)"}
#| content: valuebox
#| title: "Last updated"
list(
  icon = "clock-history",
  value = format(
    now(tzone = "America/New_York"),
    "%b. %d, '%y, %H:%M"
  )
)
```

# Team Standings

## Row {.tabset}

```{r "standings over time", fig.width=12,fig.height=5}
#| title: "Regular Season"
if (
  schedule_to_date |>
    filter(
      game_status %in%
        c(
          "Final",
          "Final OT"
        )
    ) |>
    nrow() ==
    0
) {
  value_box(
    title = "No data available",
    showcase = bs_icon(
      "hourglass-split",
      size = "6vh"
    ),
    value = tags$p(
      "No games played yet this season",
      style = "font-size: 4vh;"
    ),
    theme = "danger"
  )
} else {
  data <- roster_points_per_game |>
    lapply(
      function(x) {
        x |>
          mutate(
            earliest_game_id = schedule_to_date$game_id[1]
          ) |>
          expand(
            game_id = as.numeric(schedule_to_date$game_id),
            earliest_game_id
          ) |>
          select(
            -earliest_game_id
          ) %>%
          left_join(
            x,
            by = c(
              "game_id"
            )
          ) |>
          mutate(
            goals = ifelse(
              is.na(goals),
              0,
              goals
            ),
            assists = ifelse(
              is.na(assists),
              0,
              assists
            ),
            wins = ifelse(
              is.na(wins),
              0,
              wins
            ),
            ot_losses = ifelse(
              is.na(ot_losses),
              0,
              ot_losses
            ),
            wins = 2 * wins,
          ) %>%
          mutate(
            fantasy_points = rowSums(
              select(
                .,
                c(
                  goals,
                  assists,
                  wins,
                  ot_losses
                )
              )
            )
          ) |>
          arrange(
            game_id
          ) |>
          select(
            c(
              game_id,
              fantasy_points
            )
          ) |>
          group_by(
            game_id
          ) |>
          summarise(
            daily_scores = sum(fantasy_points)
          ) |>
          mutate(
            daily_scores = cumsum(daily_scores),
            game_id = row_number()
          )
      }
    ) |>
    bind_rows(
      .id = "Team"
    ) |>
    rename(
      "Game" = game_id,
      "Points" = daily_scores
    ) |>
    mutate(
      team_image = recode(
        Team,
        !!!team_images
      )
    ) |>
    merge(
      data.frame(
        Team = names(team_colours),
        Colours = team_colours
      )
    )

  data <- data |>
    group_by(
      Game
    ) |>
    arrange(
      desc(Points),
      Team,
      .by_group = TRUE
    ) |>
    mutate(
      Standings = row_number()
    ) |>
    ungroup()

  data |>
    ggplot() +
    geom_line(
      aes(
        x = Game,
        y = Standings,
        colour = Colours
      ),
      linewidth = 2
    ) +
    geom_point(
      data = data |>
        filter(
          Game == max(Game)
        ),
      aes(
        x = Game,
        y = Standings,
        colour = Colours
      ),
      size = 15
    ) +
    geom_image(
      data = data |>
        filter(
          Game == max(Game)
        ),
      aes(
        x = Game,
        y = Standings,
        image = team_image
      )
    ) +
    scale_color_identity() +
    scale_y_reverse() +
    guides(colour = guide_legend(override.aes = list(size = 10))) +
    theme_minimal() +
    theme(
      axis.text.y = element_blank(),
      plot.background = element_rect(fill = "#e0e0e0")
    )
}
```

```{r "standings over time preseason", fig.width=12,fig.height=5}
#| title: "Pre-season"
if (
  schedule_to_date_preseason |>
    filter(
      game_status %in%
        c(
          "Final",
          "Final OT"
        )
    ) |>
    nrow() ==
    0
) {
  value_box(
    title = "No data available",
    showcase = bs_icon(
      "hourglass-split",
      size = "6vh"
    ),
    value = tags$p(
      "No games played yet this season",
      style = "font-size: 4vh;"
    ),
    theme = "danger"
  )
} else {
  data <- roster_points_per_game_preseason |>
    lapply(
      function(x) {
        x |>
          mutate(
            earliest_game_id = schedule_to_date_preseason$game_id[1]
          ) |>
          expand(
            game_id = as.numeric(schedule_to_date_preseason$game_id),
            earliest_game_id
          ) |>
          select(
            -earliest_game_id
          ) %>%
          left_join(
            x,
            by = c(
              "game_id"
            )
          ) |>
          mutate(
            goals = ifelse(
              is.na(goals),
              0,
              goals
            ),
            assists = ifelse(
              is.na(assists),
              0,
              assists
            ),
            wins = ifelse(
              is.na(wins),
              0,
              wins
            ),
            ot_losses = ifelse(
              is.na(ot_losses),
              0,
              ot_losses
            ),
            wins = 2 * wins,
          ) %>%
          mutate(
            fantasy_points = rowSums(
              select(
                .,
                c(
                  goals,
                  assists,
                  wins,
                  ot_losses
                )
              )
            )
          ) |>
          arrange(
            game_id
          ) |>
          select(
            c(
              game_id,
              fantasy_points
            )
          ) |>
          group_by(
            game_id
          ) |>
          summarise(
            daily_scores = sum(fantasy_points)
          ) |>
          mutate(
            daily_scores = cumsum(daily_scores),
            game_id = row_number()
          )
      }
    ) |>
    bind_rows(
      .id = "Team"
    ) |>
    rename(
      "Game" = game_id,
      "Points" = daily_scores
    ) |>
    mutate(
      team_image = recode(
        Team,
        !!!team_images
      )
    ) |>
    merge(
      data.frame(
        Team = names(team_colours),
        Colours = team_colours
      )
    )

  data <- data |>
    group_by(
      Game
    ) |>
    arrange(
      desc(Points),
      Team,
      .by_group = TRUE
    ) |>
    mutate(
      Standings = row_number()
    ) |>
    ungroup()

  data |>
    ggplot() +
    geom_line(
      aes(
        x = Game,
        y = Standings,
        colour = Colours
      ),
      linewidth = 2
    ) +
    geom_point(
      data = data |>
        filter(
          Game == max(Game)
        ),
      aes(
        x = Game,
        y = Standings,
        colour = Colours
      ),
      size = 15
    ) +
    geom_image(
      data = data |>
        filter(
          Game == max(Game)
        ),
      aes(
        x = Game,
        y = Standings,
        image = team_image
      )
    ) +
    scale_color_identity() +
    scale_y_reverse() +
    guides(colour = guide_legend(override.aes = list(size = 10))) +
    theme_minimal() +
    theme(
      axis.text.y = element_blank(),
      plot.background = element_rect(fill = "#e0e0e0")
    )
}
```

## Row {.tabset}

```{r "standings full"}
#| title: "Regular season"
standings |>
  arrange(
    desc(
      Points
    )
  ) |>
  mutate(
    Change = case_when(
      Change == "-1" ~ "arrow-down",
      Change == "0" ~ NA,
      Change == "1" ~ "arrow-up"
    )
  ) |>
  gt() |>
  fmt_icon(
    columns = Change,
    fill_color = c(
      "arrow-up" = "#128800ff",
      "arrow-down" = "#c50101ff",
      height = "1.5em"
    )
  ) |>
  text_transform(
    locations = cells_body(
      columns = Team
    ),
    fn = function(x) {
      web_image(
        url = x,
        height = "5vh"
      )
    }
  ) |>
  tab_style(
    style = list(
      cell_fill(color = from_column(column = "Colours")),
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Team
    )
  ) |>
  cols_hide(Colours) |>
  cols_align(
    columns = everything(),
    align = "center"
  ) |>
  sub_missing(
    columns = everything(),
    rows = everything(),
    missing_text = ""
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }

    .gt_col_heading {
      position: sticky !important;
      top: 0px !important;
      z-index: 10 !important;
    }
    "
  )
```

```{r "standings full preseason"}
#| title: "Pre-season"
standings_preseason |>
  arrange(
    desc(
      Points
    )
  ) |>
  mutate(
    Change = case_when(
      Change == "-1" ~ "arrow-down",
      Change == "0" ~ NA,
      Change == "1" ~ "arrow-up"
    )
  ) |>
  gt() |>
  fmt_icon(
    columns = Change,
    fill_color = c(
      "arrow-up" = "#128800ff",
      "arrow-down" = "#c50101ff",
      height = "1.5em"
    )
  ) |>
  text_transform(
    locations = cells_body(
      columns = Team
    ),
    fn = function(x) {
      web_image(
        url = x,
        height = "5vh"
      )
    }
  ) |>
  tab_style(
    style = list(
      cell_fill(color = from_column(column = "Colours")),
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Team
    )
  ) |>
  cols_hide(Colours) |>
  cols_align(
    columns = everything(),
    align = "center"
  ) |>
  sub_missing(
    columns = everything(),
    rows = everything(),
    missing_text = ""
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }

    .gt_col_heading {
      position: sticky !important;
      top: 0px !important;
      z-index: 10 !important;
    }
    "
  )
```

# Team Rosters

::: {.panel-tabset}

```{r "team rosters"}
#| output: asis
res <- purrr::map_chr(
  unique(names(team_rosters)),
  function(name) {
    knitr::knit_child(
      text = c(
        "## `r name`",
        "",
        "```{r}",
        "#| echo: false",
        "html(",
        "    web_image(",
        "        url = standings |>",
        "          filter(",
        "            Name == name",
        "          ) |>",
        "          select(",
        "            Team",
        "          ) |>",
        "          pull(),",
        "        height = '50px'",
        "    )",
        ")",
        "",
        "generate_pwhl_roster_gt_table(",
        "    name,",
        "    team_rosters,",
        "    fantasy_roster_points,",
        "    schedule",
        ")",
        "",
        "```",
        "",
        ""
      ),
      envir = environment(),
      quiet = TRUE
    )
  }
)

cat(res, sep = '\n')
```
:::

# Team Rosters (Pre-season)

::: {.panel-tabset}

```{r "team rosters preseason"}
#| output: asis
res <- purrr::map_chr(
  unique(names(team_rosters)),
  function(name) {
    knitr::knit_child(
      text = c(
        "## `r name`",
        "",
        "```{r}",
        "#| echo: false",
        "html(",
        "    web_image(",
        "        url = standings |>",
        "          filter(",
        "            Name == name",
        "          ) |>",
        "          select(",
        "            Team",
        "          ) |>",
        "          pull(),",
        "        height = '50px'",
        "    )",
        ")",
        "",
        "generate_pwhl_roster_gt_table(",
        "    name,",
        "    team_rosters_preseason,",
        "    fantasy_roster_points_preseason,",
        "    schedule",
        ")",
        "",
        "```",
        "",
        ""
      ),
      envir = environment(),
      quiet = TRUE
    )
  }
)

cat(res, sep = '\n')
```
:::

# Schedule

## Row {.tabset}

```{r "schedule"}
#| title: "Regular season"
schedule |>
  select(
    c(
      game_date,
      game_status,
      away_team_logo,
      away_score,
      home_team_logo,
      home_score
    )
  ) |>
  mutate(
    game_date = as.Date(
      game_date,
      format = "%Y-%m-%d"
    ) |>
      format(
        "%a, %b %e"
      )
  ) |>
  gt() |>
  fmt_image(
    columns = c(
      away_team_logo,
      home_team_logo
    )
  ) |>
  cols_align(
    align = "center",
    columns = c(
      game_status,
      away_score,
      home_score
    )
  ) |>
  cols_width(
    game_date ~ pct(20),
    game_status ~ pct(20),
    away_team_logo ~ pct(10),
    away_score ~ pct(10),
    home_team_logo ~ pct(10),
    home_score ~ pct(10)
  ) |>
  cols_label(
    game_date = "Date",
    game_status = "Time",
    away_team_logo = "Away",
    away_score = "Score",
    home_team_logo = "Home",
    home_score = "Score"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }

    .gt_col_heading {
      position: sticky !important;
      top: 0px !important;
      z-index: 10 !important;
    }
    "
  )
```

```{r "schedule preseason"}
#| title: "Pre-season"
schedule_preseason |>
  select(
    c(
      game_date,
      game_status,
      away_team_logo,
      away_score,
      home_team_logo,
      home_score
    )
  ) |>
  mutate(
    game_date = as.Date(
      game_date,
      format = "%Y-%m-%d"
    ) |>
      format(
        "%a, %b %e"
      )
  ) |>
  gt() |>
  fmt_image(
    columns = c(
      away_team_logo,
      home_team_logo
    )
  ) |>
  cols_align(
    align = "center",
    columns = c(
      game_status,
      away_score,
      home_score
    )
  ) |>
  cols_width(
    game_date ~ pct(20),
    game_status ~ pct(20),
    away_team_logo ~ pct(10),
    away_score ~ pct(10),
    home_team_logo ~ pct(10),
    home_score ~ pct(10)
  ) |>
  cols_label(
    game_date = "Date",
    game_status = "Time",
    away_team_logo = "Away",
    away_score = "Score",
    home_team_logo = "Home",
    home_score = "Score"
  ) |>
  tab_options(
    table.background.color = "#F5F5F5",
    column_labels.background.color = "#2B2D42",
    table.font.size = px(16),
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    table_body.hlines.color = "transparent",
    table_body.border.bottom.color = "transparent",
    column_labels.border.bottom.color = "transparent",
    column_labels.border.top.color = "transparent"
  ) |>
  tab_style_body(
    style = cell_borders(
      sides = c("top", "right", "left", "bottom"),
      weight = px(0) # Remove row borders
    ),
    fn = function(x) {
      is.numeric(x) | is.character(x)
    }
  ) |>
  opt_css(
    css = "

    table tr:nth-child(odd) {
      background-color: #e0dedeff;
    }

    .gt_col_heading {
      position: sticky !important;
      top: 0px !important;
      z-index: 10 !important;
    }
    "
  )
```


# Team Generator {#team-generator}

Select one of the rows in this table to use (or take some inspo from)

```{r "random team generator"}
seed <- 1

random_teams <- data.frame(matrix(ncol = 12, nrow = 0)) |>
  set_names(
    "F1",
    "F2",
    "F3",
    "F4",
    "F5",
    "F6",
    "D1",
    "D2",
    "D3",
    "D4",
    "G1",
    "G2"
  )

for (i in 1:50) {
  random_team <- all_teams |>
    mutate(
      position = case_when(
        position == "C" ~ "F",
        position == "LW" ~ "F",
        position == "RW" ~ "F",
        position == "LD" ~ "D",
        position == "RD" ~ "D",
        .default = position
      )
    ) |>
    group_by(position) |>
    slice_sample(
      n = 6
    ) |>
    ungroup()

  random_teams <- rbind(
    random_teams,
    rbind(
      random_team |> filter(position == "F") |> select(player_name),
      random_team |>
        filter(position == "D") |>
        slice(1:4) |>
        select(player_name),
      random_team |>
        filter(position == "G") |>
        slice(1:2) |>
        select(player_name)
    ) |>
      transpose() |>
      set_names(
        "F1",
        "F2",
        "F3",
        "F4",
        "F5",
        "F6",
        "D1",
        "D2",
        "D3",
        "D4",
        "G1",
        "G2"
      )
  )
}

random_teams <- cbind(
  Team_name = slice_sample(read.csv("static/common_words.csv"), n = 50),
  Team_colour = sample(
    rgb(
      t(col2rgb(colors())),
      maxColorValue = 255
    ),
    50
  ),
  random_teams
)

library(DT)

random_teams |> datatable()
```

# Draft Info

## Row

::: {.card title="Rules"}
Choose your fantasy team name, colour, logo and roster in the [Google Sheet](https://docs.google.com/spreadsheets/d/1sywjZ6quCmbLBq_wEEXZEDzcW0NeBpCtRaT3W1hDkhI/edit?usp=sharing). (If you want some inspiration for your draft, you can check out the [team generator](#team-generator))<br>
&nbsp;&nbsp;&nbsp;&nbsp;🔴🟡🔵**Team Colour:** Valid hexadecimal colour code<br>
&nbsp;&nbsp;&nbsp;&nbsp;👩‍👩‍👧📷🖥️**Team Image:** Valid link to any image on the web<br><br>
Your team should have exactly the following (the Google Sheet dropdowns force this structure, don't worry!):<br>
&nbsp;&nbsp;&nbsp;&nbsp;**🏒 6 forwards**<br>
&nbsp;&nbsp;&nbsp;&nbsp;**🛡️ 4 defenders**<br>
&nbsp;&nbsp;&nbsp;&nbsp;**🥅 2 goalies**<br><br>
😮‍💨 Players/goalies aren't restricted to a single fantasy team so if someone took a player you like, you can take them too!<br><br>
↔️ **Trades:** Throughout the season, you are allowed **exactly 1 trade** (respecting the team structure). Your new player only contributes points to your fantasy score starting the day after the trade. Please **let Alex or Noah know directly** if/when you make a trade!<br><br>
🕐 **Deadline:** You can use all of November's pre-season and regular season games to scout your roster and aim to lock it in by **November 30th, 2025**! After this date, the Google Sheet will be 👁️**View Only**👁️<br><br>
💰💵💸 **Prize pool (Optional):** E-transfer $10 to Alex or Noah to enter in the fantasy prize pool! More information TBD but you could **WIN BIGGGG! (Send an e-transfer or intent to e-transfer by the roster deadline to enter the prize pool)**
:::

## Row

::: {.card title="Scoring"}
Your fantasy team's score is updated daily with data from the previous day's games. Each day, each member of your fantasy roster will contribute a number of points to your team's overall score, following the scheme below:

🏒 1 point per goal<br>
🤝 1 point per assist<br>
✨ 2 points per win\*<br>
😖 0 points per loss\*<br>
🥇 1 point per OT loss\*

You can check how your and everyone else's teams are doing [here](#team-standings). Note that eventually, only **regular season games** will contribute to your fantasy teams score.

\*Note that if your play did not play in a game in which their team won, they will *not* contribute points to your score (this includes dressed goalies that did not get subbed in).
:::