---
title: "Fantasy Draft Data"
execute:
  echo: false
  warning: false
  error: false
---

```{r "imports"}
library(tidyverse)
library(DT)
```

```{r "source"}
source("./R/assign_fantasy_draft_value_2025.R")
source("./R/assign_fantasy_draft_value_2026.R")
```

For the 2026-2027 season, we are making two changes to changes to the fantasy league regarding fantasy points and fantasy team drafting. First, the new structure for scoring fantasy points is as follows:

| Skaters        | Goalies |
| ------------- |-------------|
| 🏒 2 pts/goal<br>🤝 1 pt/assist<br>🎯 0.1 pts/shot<br>⛔ 0.1 pts/blocked shot<br>✨ 2 pts/win<br>😖 0 pts/loss<br>🥇 1 pt/OT loss      | 🧱 1 pt/shutout<br>⛔ 0.05 pts/save<br>✨ 2 pts/win<br>😖 0 pts/loss<br>🥇 1 pt/OT loss |

Second, all PWHL players will be assigned a **Fantasy Draft Value (FDV)**, and a **Value Cap** will be imposed to the fantasy teams that will be drafted this year. The FDV will be computed based on the new fantasy point structure applied retroactively to the 2025-2026 season.

# 2026-2027 Season

```{r "2025 - variables"}

fantasy_draft_values_season_5 <- readRDS(
    "fantasy_draft_values_season_5.rds"
)

fantasy_points_season_8 <- readRDS(
  "fantasy_points_season_8.rds"
)

fantasy_teams_season_8 <- readRDS(
  "fantasy_teams_season_8.rds"
)

fantasy_draft_values_season_8 <- readRDS(
  "fantasy_draft_values_season_8.rds"
)
```

## Assigning the FDV

The FDV will be assigned differently based on whether the player is a new rookie in the upcoming season. In each case however, instead of looking at **Fantasy Points (FP)** earned last year, we look at the **Projected Fantasy Points (PFP)** earned last year. The PFP are defined as follows:

$$
\text{PFP} = 30 * \frac{\text{FP}}{\text{GP}},
$$

where $GP:=$ games played.

We take the average number of FP earned per game played and multiply that by the total number of games in a season for one team (30) to estimate how many FP would have been earned if the player played every game of the season.

### Non-rookie

If the player is not a rookie, the FDV is is simply the player's earned PFP last season, rounded to the nearest integer.

```{r "fdv for non-rookies"}
fantasy_draft_values_season_8 |>
  filter(
    rookie %in% c(0,1)
  ) |>
  left_join(
    fantasy_points_season_8 |>
      select(
        name,
        fantasy_points
      ),
    by = "name"
  ) |>
  select(
    name,
    fantasy_points,
    projected_fantasy_points,
    fantasy_draft_value
  ) |>
  mutate(
    across(
      where(is.numeric),
      \(x) round(x, digits = 2)
    )
  ) |>
  arrange(
    desc(fantasy_draft_value),
    name
  ) |>
  datatable(
    colnames = c(
      "Name" = "name",
      "FP" = "fantasy_points",
      "PFP" = "projected_fantasy_points",
      "FDV" = "fantasy_draft_value"
    )
  )
```

### Rookie

After last season, all of the rookies of that season have accumulated fantasy points from their performance (duh). We will look at two plots. First, a scatter plot of PFPs earned by overall draft position:

::: {.panel-tabset}

##### Plot

```{r "rookie PFP by overall draft position - 2025/2026 (scatter plot)"}
fantasy_points_season_8 |>
  filter(
    rookie == 1
  ) |>
  left_join(
    fantasy_draft_values_season_5 |>
      filter(
        rookie == -1
      ) |>
      select(
        name,
        overall_draft_position
      ),
      by = "name"
  ) |>
  filter(
    !is.na(overall_draft_position)
  ) |>
  arrange(
    overall_draft_position
  ) %>%
  ggplot(
    aes(
      x = overall_draft_position,
      y = projected_fantasy_points
    )
  ) +
  geom_point()
```

##### Table

```{r "rookie PFP by overall draft position - 2025/2026 (table)"}
fantasy_points_season_8 |>
  filter(
    rookie == 1
  ) |>
  left_join(
    fantasy_draft_values_season_5 |>
      filter(
        rookie == -1
      ) |>
      select(
        name,
        overall_draft_position
      ),
      by = "name"
  ) |>
  mutate(
    projected_fantasy_points = round(
      projected_fantasy_points,
      digits = 2
    )
  ) |>
  filter(
    !is.na(overall_draft_position)
  ) |>
  arrange(
    overall_draft_position,
    name
  ) |>
  select(
    name,
    overall_draft_position,
    projected_fantasy_points
  ) |>
  datatable(
    colnames = c(
      "Name" = "name",
      "Draft No." = "overall_draft_position",
      "PFP" = "projected_fantasy_points"
    )
  )
```

:::

There is clearly not a perfect correlation between PFP and overall draft position, but this is expected. However, there is a general trend of higher PFPs as overall draft position is lowered.

```{r "Fit linear model to PFPs descending"}
model <- fantasy_draft_values_season_8 |>
  filter(
    rookie == 1
  ) |>
  mutate(
    projected_fantasy_points = if_else(
      projected_fantasy_points < exp(1),
      exp(1),
      projected_fantasy_points
    ),
    log_projected_fantasy_points = log(projected_fantasy_points)
  ) |>
  arrange(
    desc(log_projected_fantasy_points)
  ) %>%
  lm(
    log_projected_fantasy_points ~ seq_len(
      nrow(
        .
      )
    ),
    data = .
  )

theoretical_line <- function(x) {
 exp(
   coef(model)[[1]] +
     coef(model)[[2]] * x
 )
}
```

On the other hand, when looking at PFPs earned sorted in descending order, we get a beautiful exponential distribution:

#### 2. PFPs earned, sorted in descending order

::: {.panel-tabset}

##### Plot

```{r "rookie PFP descending with exponential curve - 2025/2026 (scatter plot)"}
fantasy_draft_values_season_8 |>
  filter(
    rookie == 1
  ) |>
  arrange(
    desc(projected_fantasy_points)
  ) %>%
  ggplot(
    aes(
      x = seq_len(
        nrow(
          .
        )
      ),
      y = projected_fantasy_points
    )
  ) +
  geom_point() +
  geom_function(fun = theoretical_line)
```

##### Table

```{r "rookie PFP descending - 2025/2026 (table)"}
fantasy_points_season_8 |>
  filter(
    rookie == 1
  ) |>
  left_join(
    fantasy_draft_values_season_5 |>
      filter(
        rookie == -1
      ) |>
      select(
        name,
        overall_draft_position
      ),
      by = "name"
  ) |>
  mutate(
    projected_fantasy_points = round(
      projected_fantasy_points,
      digits = 2
    )
  ) |>
  arrange(
    desc(projected_fantasy_points),
    name
  ) |>
  select(
    name,
    overall_draft_position,
    projected_fantasy_points
  ) |>
  datatable(
    colnames = c(
      "Name" = "name",
      "Draft No." = "overall_draft_position",
      "PFP" = "projected_fantasy_points"
    )
  )
```

:::

::: {.callout-note}
We secretly replaced all PFPs less than $\mathrm{e}$ with $\mathrm{e}$, just so that the exponential fit would never yield negative values. You'll see why soon...
:::

Rather than using PFPs by overall draft position for the last season, we are going to use the exponential curve approximating the PFPs descending in order to inform how the FDVs get assigned to the rookies in the upcoming season. The formula for the FDV for new rookies will be as follows:

$$
\text{FDV} = \max\left( \text{round}\left(\exp \left( b + m\cdot\left(1+(\text{pos}_\text{draft} - 1)\cdot\frac{\text{N}_\text{rookies,t-1}-1}{\text{N}_\text{rookies,t}}\right)\right)\right), 1\right),
$$

where:

- $\text{pos}_\text{draft}\in\{1,\ldots,\text{N}_\text{rookie,t}\}:=$ draft order position of new rookie
- $\text{N}_\text{rookies,t}:=$ number of new rookies in year $t$ (this year)
- $\text{N}_\text{rookies,t-1}:=$ number of new rookies in year $t-1$ (last year)
- $b:=$ intercept of the line fit to the $\log$ of the descending PFPs ($b=$ `{r} coef(model)[[1]]`)
- $m:=$ slope of the line fit to the $\log$ of the descending PFPs ($m=$ `{r} coef(model)[[2]]`)

The idea behind this formula is that we map $\text{N}_\text{rookies,t}$ equal points to the support of the fit exponential curve, which is $\{1,\ldots,\text{N}_\text{rookie,t-1}\}$. Under this mapping, the first overall draft pick (K.K. Harvey for the 2026-2027 season) should be mapped to the PFP estimate corresponding to the first overall draft pick of the 2025-2026 season (Kristýna Kaltounková), the last overall draft pick for the 2026-2027 season should be mapped to the PFP estimate corresponding to the last overall draft pick of the 2025-2026 season, and each draft pick in between for the 2026-2027 season should be evenly spaced out between $1$ and $\text{N}_\text{rookie,t-1}$; this yields a spacing of $\frac{\text{N}_\text{rookies,t-1}-1}{\text{N}_\text{rookies,t}}$

The FDVs for the new rookies of the 2026-2027 season are therefore:

```{r "fdv for rookies"}
fantasy_draft_values_season_8 |>
  filter(
    rookie == -1
  ) |>
  arrange(
    overall_draft_position,
    name
  ) |>
  select(
    name,
    overall_draft_position,
    fantasy_draft_value
  ) |>
  datatable(
    colnames = c(
      "Name" = "name",
      "Draft No." = "overall_draft_position",
      "FDV" = "fantasy_draft_value"
    )
  )
```

## Value Cap

Preliminary value cap: Find the 75th percentile of FDVs by position and multiply these by the number of allotted slots per position, respectively. The percentiles are as follows:

```{r "fdv percentiles"}
fantasy_draft_values_season_8 |>
  drop_na(position) |>
  group_by(
    position
  ) |>
  summarise(
    q725= quantile(
      fantasy_draft_value,
      probs = 0.25
    ),
    median = median(fantasy_draft_value),
    mean = mean(fantasy_draft_value),
    q75 = quantile(
      fantasy_draft_value,
      probs = 0.75
    )
  ) |>
  arrange(
    factor(
      position,
      levels = c("F","D","G")
    )
  ) |>
  datatable()
```

Therefore, the salary cap is computed as `6*(26) + 4*(22) + 2*(22.25) = 288.5`, which we will round up to a nice clean `300`.

# 2025-2026 Season

We can check how this process for assigning FDVs compares against actual FP earned by computing FDVs for the 2025-2026 roster based on the 2024-2025 season and then aggregating all PFP/FP earned during the 2025-2026 season.

## FP/PFP vs. FDV

::: {.panel-tabset}

### Non-rookies

```{r "fp/pfp vs fdv - non-rookies"}
fantasy_draft_values_season_5 |>
  left_join(
    fantasy_points_season_8 |>
      select(
        name,
        position,
        fantasy_points
      ),
    by = c(
      "name",
      "position"
    )
  ) |>
  filter(
    rookie == 0
  ) |>
  select(
    name,
    fantasy_draft_value,
    fantasy_points
  ) |>
  mutate(
    payoff_net = fantasy_points - fantasy_draft_value,
    payoff_factor = fantasy_points/fantasy_draft_value,
    across(
      where(is.numeric),
      \(x) round(
        x,
        digits = 2
      )
    )
  ) |>
  arrange(
    desc(fantasy_draft_value),
    name
  ) |>
  datatable(
    colnames = c(
      "Name" = "name",
      "FDV" = "fantasy_draft_value",
      "FP" = "fantasy_points",
      "FP-FDV" = "payoff_net",
      "FP/FDV" = "payoff_factor"
    )
  )
```

### Rookies

```{r "fp/pfp vs fdv - rookies"}
fantasy_draft_values_season_5 |>
  filter(
    rookie == -1
  ) |>
  left_join(
    fantasy_points_season_8 |>
      select(
        name,
        position,
        fantasy_points
      ),
    by = c(
      "name",
      "position"
    )
  ) |>
  select(
    name,
    overall_draft_position,
    fantasy_draft_value,
    fantasy_points
  ) |>
  mutate(
    payoff_net = fantasy_points - fantasy_draft_value,
    payoff_factor = fantasy_points/fantasy_draft_value,
    across(
      where(is.numeric),
      \(x) round(
        x,
        digits = 2
      )
    )
  ) |>
  arrange(
    desc(fantasy_draft_value),
    name
  ) |>
  datatable(
    colnames = c(
      "Name" = "name",
      "Draft No." = "overall_draft_position",
      "FDV" = "fantasy_draft_value",
      "FP" = "fantasy_points",
      "FP-FDV" = "payoff_net",
      "FP/FDV" = "payoff_factor"
    )
  )
```

:::
<!--
## PFP over FDV - Scatter plot and Line of Best Fit

::: {.panel-tabset}

### Rookie Status

```{r "2025 - plots: rookie status"}

data <- fantasy_draft_values_season_5 |>
  inner_join(
    fantasy_points_season_8 |>
      select(
        name,
        position,
        fantasy_points
      ),
    by = c(
      "name",
      "position"
    )
  ) |>
  select(
    name,
    rookie,
    position,
    fantasy_draft_value,
    projected_fantasy_points,
    fantasy_points
  )

ggplot(
  data,
  aes(
    x = fantasy_draft_value
  )
) +
  geom_point(
    aes(
      y = fantasy_points,
      colour = factor(rookie)
    ),
    size = 3
  ) +
  geom_smooth(
    data = \(df) filter(df,rookie==1),
    aes(
      y = fantasy_points
    ),
    method="lm",
    se=TRUE,
    col="blue"
  ) +
  geom_smooth(
    data = \(df) filter(df,rookie==0),
    aes(
      y = fantasy_points
    ),
    method="lm",
    se=TRUE,
    col="red"
  ) +
  geom_line(
    aes(
      y = fantasy_draft_value
    )
  )
```

### Position

```{r "2025 - plots: position"}
ggplot(
  data,
  aes(
    x = fantasy_draft_value
  )
) +
  geom_point(
    aes(
      y = fantasy_points,
      colour = factor(position)
    ),
    size = 3
  ) +
  geom_smooth(
    data = \(df) filter(df,position == "F"),
    aes(
      y = fantasy_points
    ),
    method="lm",
    se=TRUE,
    col="green"
  ) +
  geom_smooth(
    data = \(df) filter(df,position == "D"),
    aes(
      y = fantasy_points
    ),
    method="lm",
    se=TRUE,
    col="red"
  ) +
  geom_smooth(
    data = \(df) filter(df,position == "G"),
    aes(
      y = fantasy_points
    ),
    method="lm",
    se=TRUE,
    col="blue"
  ) +
  geom_line(
    aes(
      y = fantasy_draft_value
    )
  )
```

::: -->

## Fantasy teams

Suppose the teams that were drafted during the 2025-2026 fantasy season included the FDVs for that season. We can compare the sum of these FDVs, representing the 'cost' of the fantasy team, against the FP output of the team throughout the season.

```{r "fantasy team comparison"}
lapply(
  names(fantasy_teams_season_8),
  function(fantasy_team_name) {

    bind_rows(
      fantasy_teams_season_8[[fantasy_team_name]]$roster$skaters |>
        select(
          name,
          team_code,
          rookie,
          fantasy_points
        ) |>
        left_join(
          fantasy_draft_values_season_5,
          by = "name"
        ),
      fantasy_teams_season_8[[fantasy_team_name]]$roster$goalies |>
        select(
          name,
          team_code,
          rookie,
          fantasy_points
        ) |>
        left_join(
          fantasy_draft_values_season_5,
          by = "name"
        )
    ) |>
      mutate(
        fantasy_team_name = fantasy_team_name
      )
  }
) |>
  bind_rows() |>
  group_by(
    fantasy_team_name
  ) |>
  summarise(
    fantasy_draft_value = sum(fantasy_draft_value),
    fantasy_points = sum(fantasy_points)
  ) |>
  mutate(
    point_gain = fantasy_points - fantasy_draft_value,
    across(
      where(is.numeric),
      round,
      digits = 2
    )
  ) |>
  arrange(
    desc(fantasy_points),
    fantasy_team_name
  ) |>
  datatable(
    colnames = c(
      "Team" = "fantasy_team_name",
      "FDV" = "fantasy_draft_value",
      "FP" = "fantasy_points",
      "Gain" = "point_gain"
    )
  )
```
